\section{Related Work}
\label{sec:related-work}

In this section, we discuss studies of  regression testing focusing on 
test case prioritization techniques that are most closely 
related to our work. Further, we discuss recommender systems 
and research related to that topic.

\subsubsection*{Test Case Prioritization}
Test case prioritization techniques reorder test cases to maximize
some objective functions, such as detecting defects as early as possible.
Due to the appealing benefits of test case prioritization in practice, 
many researchers and practitioners
have proposed and studied various test case prioritization 
techniques. For example, these techniques help engineers discover faults
early in testing, which allows them to begin debugging earlier.
In this case, entire test suites may still be executed, which avoids 
the potential drawbacks associated with omitting test cases. 
Recent surveys ~\cite{catal13, marksurvey} provide a comprehensive 
understanding of overall trends of the techniques and suggest areas for improvement.

Depending on the types of information available, various test case
prioritization techniques can be utilized, but 
the majority of prioritization techniques have used source code
information to implement the techniques.
For instance, many researchers have utilized code coverage information
to implement prioritization techniques~\cite{elbaum02feb, kim02may,rothermel01oct}. Although this approach is simple and na\"ive, many empirical
studies have shown that this approach can be effective~\cite{cost3, 
	cost1, Malishevsky02, myra}.
Recent prioritization techniques have used other
types of code information, such as slices~\cite{jeffrey06sep}, change
history~\cite{sherriff07}, code modification information, and fault
proneness of code~\cite{mirarab07}.

More recently, several prioritization techniques 
utilizing other types of information have also been proposed. 
For example, Anderson et al.  applied telemetry data to compute fingerprints 
to extract usage patterns and for test prioritization~\cite{jeff16}.
Memon and Amalfitano performed a study in which they applied telemetry 
data to generate usage pattern profiles~\cite{memongui}.  
In another study, Amalfitano et al. built finite state models
based on usage data that they collected from rich Internet applications ~\cite{rich}. 
Carlson et al.~\cite{ryan} presented clustering-based techniques that
utilize real fault history information including code coverage.
Anderson et al.~\cite{jeff14} investigated the use of various code features
mined from a large software repository to improve regression testing techniques.
Gethers et al. presented a method  that uses textual change of source code
to estimate an impact set ~\cite{kagdichange}. 

\subsubsection*{Context-aware Recommender system}
Recommender systems are software engineering tools that make 
the decision making process easier by providing a list of relevant items.
There are three primary  categories in recommender systems:
content-based algorithms, collaborative filtering algorithms, and hybrid approaches ~\cite{recomsurvey05}.  
Recommender systems are commonly used by users in their daily routines, 
helping in such tasks as finding 
their target items more easily.
Some widely-used applications that provide recommender systems
are Amazon, Facebook, and Netflix. These applications provide suggestions
to target users based on the user or item characteristic similarities.  

Further, in the area of software engineering, due to the decline in hardware 
facility prices, a variety of information is collected by software 
providers, such as change history, issue reports and databases, user log files, 
and so on.
With the fast growth of such information, machine learning technologies  
motivate software engineers to apply recommendation systems in software 
development. Recommender systems in software engineering have been applied  
to improve software quality and to address the challenges of development process~\cite{rssebook}.  
For instance, Murakami et al. ~\cite{murakami} proposed a technique that 
uses user editing activities  detecting code relevant to existing methods. 
Christidis et al. ~\cite{costas} implemented a recommender system 
to display developer activities by using information artifacts with quantitative metrics. 
Danylenko and Lowe provided a context-aware recommender system 
to automate a decision-making process for determining the efficiency of 
non-functional requirements ~\cite{contextawar}.

As we discussed briefly, there are many types of information available 
for implementing test case prioritization techniques.
In this research, we collected over 2,000 user sessions from 
three different web applications and gathered the change history of each application. 
Our research seeks to apply item-based collaborative filtering algorithms 
to generate a recommendation list of test cases for 
test prioritization.
To our knowledge, our recommender system-based prioritization technique is novel 
and has not yet been explored in the regression testing area.



% add more content about context aware recom sys





